### 2018-03-29 Sections/cryptowars.tex
Economics update

The mining process is based upon the computational hardness of inverting (double) SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	\epsilon_\text{lower}\leq \text{SHA256}(\text{SHA256}(x_\text{coin})) \leq \epsilon_\text{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist. This technique is known as `proof-of-work'\index{Proof-of-work}, for associating something of value with proof that certain amounts of computation were required to achieve it. This idea was originally borrowed from the Hashcash protocol\index{Hashcash}, where proof-of-work is employed to associate work (and hence monetary value) with sending emails so as to eliminate automated spamming bots.

>>>>

The mining process is based upon the computational hardness of inverting (double) SHA256 hashing\index{Hash functions}\index{SHA256}. A legitimate Bitcoin is defined by a string with a hash satisfying a thoughtfully chosen constraint, specifically one which hashes to a value within some range,
\begin{align}
	\epsilon_\text{lower}\leq \text{SHA256}(\text{SHA256}(x_\text{coin})) \leq \epsilon_\text{upper}.
\end{align}
This is slightly weaker than inverting hash functions, but is nonetheless a task that can only be approached via brute-force hashing in the forward direction. This associates computational complexity with the mining process, and hence computational integrity of the money supply, whilst upper bounding the number of unique coins that can exist. This technique is known as `proof-of-work'\index{Proof-of-work}, for associating something of value with proof that certain amounts of computation were required to achieve it\footnote{In future implementations of Blockchain protocols, the proof-of-work required for a given protocol can be arbitrarily manipulated to accommodate for technological changes in computational power, for example via the adoption of quantum computing. The amount of work required to satisfy the constraint grows exponentially as we narrow the range \mbox{$\epsilon_\text{upper}-\epsilon_\text{lower}$}, providing us with much leverage to manipulate the complexity of proof-of-work, and hence the rate of inflation\index{Inflation rate} in the money supply.}. This idea was originally borrowed from the Hashcash protocol\index{Hashcash}, where proof-of-work is employed to associate work (and hence monetary value) with sending emails so as to eliminate automated spamming bots.

### 2018-03-29 Sections/economics_of_the_quantum_internet.tex
Economics update

@@

We begin by defining the ratio $Q(t)$ between the economic gain from executing computations, and the cost of the physical hardware performing them,
\begin{align}
Q(t)=\frac{n_\text{gain}(t)}{n_\text{cost}(t)}.
\end{align}

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment, with \mbox{$Q\to 1$} driven ever closer to unity as market competition increases, thereby closing the gap between investment and reward,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{gain}(t) \gtrapprox n_\text{invest}(t).
\end{align}

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth})\index{Network growth postulate} and employing a combined computational scaling function\index{Combined computational scaling functions} (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is the product of the hardware cost per qubit and the number of qubits,
\begin{align}
	n_\text{invest}(t) &= N_t C_t \nonumber \\
	&= N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the time-dependent cost of computation postulate,

@@

This implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation is,
\begin{align}
L_0 \gtrapprox \frac{C_0}{f_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the initial value of computations simply approximates the initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=1$}.}\label{fig:econ_cost_of_comp}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{single_qubit_QCL}
\caption{Time-dependent quantum computational leverage for a single qubit with different computational scaling functions, under the assumption of exponential network growth with \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

The computational dividend at future time $t$, $D_t$, is masterfully baked using the same recipe as the spot price\index{Jamie Oliver}, adjusted for extrapolated qubit growth and decay in the cost of computation,
\begin{definition}[Computational dividend]\label{def:dividend_formula}
The dollar-equivalent dividend paid by a time-share in the quantum network at future time $t$, for the duration of a single unit of time, is,
\begin{align} \label{eq:dividend}\index{Dividend}
D_t &= L_t c_n(t) \nonumber \\
&= \frac{C_0 {\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)} \cdot \frac{n}{N_0 {\gamma_N}^t} \cdot f_\text{sc}(N_0 {\gamma_N}^t) \nonumber \\
&= n C_0 {\gamma_C}^{-t}.
\end{align}
\end{definition}
Note that the spot price is the dividend at time \mbox{$t=0$}.

%
% Qubit Asset Pricing Model
%

\subsection{Qubit asset pricing model}\label{sec:qubit_pricing_model}\index{Qubit asset pricing model}

The simplest transaction that might take place is the outright purchase of physical qubits. To price this asset we sum up all future computational dividends, discounted by their respective accumulation of the equivalent risk-free rate of return. We take the limit as time goes to infinity, such that we envisage holding onto the assets and receiving their dividends indefinitely into the future (i.e the computational assets are non-perishable and effectively have infinite lifespan). Then the qubit asset pricing model is,

\begin{definition}[Qubit asset pricing model] \label{def:qubit_ass_pricing}\index{Qubit asset pricing model}
The present-day spot price of a qubit asset is,	
\begin{align}
S_0 &= \sum_{t=0}^\infty D_t e^{-rt} \nonumber \\
&= n C_0 \sum_{t=0}^\infty e^{-rt} {\gamma_C}^{-t} \nonumber \\
&= n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}.
\end{align}	
\end{definition}

Thus, the spot price reflects the accumulation of future profits, in terms of computational dividends, that will be paid by the asset.

Importantly, the value of the asset is scaled by a function of the size of the network. Thus, the value of qubit assets is not objective, but is relative to the network in which they reside. This is unlike classical computing, where hardware costs are strictly objective.

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{qubit_ass_pricing_model}
\caption{\comment{To do}}\label{fig:qubit_ass_pricing_model}
\end{figure}

\comment{What's the difference between this and the hardware cost???}

%In the limit of fast network growth, \mbox{$\gamma_N\gg 1$}, we have,
%\begin{align}
%S \approx n\cdot L_0 \cdot \chi_\text{sc}(N_0).
%\end{align}

@@

The standard forward pricing model is \cite{???},
\begin{align} \label{eq:orig_for_contr} \index{Forward contract pricing model} 
F(T) = S_0 e^{rT} - \sum_{t=0}^T D_t e^{r(T-t)},
\end{align}
where,
\begin{itemize}
	\item $F(T)$ is the forward price at time $T$.\index{Forward price}
	\item $S_0$ is the spot price at time \mbox{$t=0$} (i.e present-day value).
	\item $T$ is the time of maturity, at which time the contract is executed and the transaction is made.\index{Maturity}
	\item $r$ is the risk-free rate of return. \index{Risk-free rate of return}
	\item The usual cost of carry, $q$, is neglected. We assume this is zero since maintenance of physical computer assets is somewhat negligible and the goods are effectively non-perishable. Furthermore, in the context of a global network, transactions may be executed entirely over the network, with no direct exchange in physical assets, making transactions very transparent and liquid, with little transaction overhead.\index{Cost of carry}
	\item $D_t$ is the expected dividend at time $t$. In our case this will be the dollar-equivalent value of units of computation.\index{Dividend}
\end{itemize}

@@

In our case, the spot price is that given by the qubit asset pricing model, and the dividends are the computational dividends in dollars. Then, from Eq.~(\ref{eq:orig_for_contr}), the forward price for qubits is,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in qubits is,
\begin{align}
F(T) &= e^{rT} \sum_{t=T+1}^\infty D_t e^{-rt} \nonumber \\
&= n C_0 e^{rT} \sum_{t=T+1}^\infty e^{-rt} {\gamma_C}^{-t} \nonumber \\
&= n C_0 \frac{e^{-rT}{\gamma_C}^{-T}}{e^{r}\gamma_C-1}.
\end{align}
\end{definition}
\comment{To do. Why no dependence on fsc or gammaN?}

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod}
\caption{Forward contract price on a single physical qubit to be delivered at time $T$ in the future. Units are \mbox{$C_0=1$}.}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

The return on investment (RoI) is a means by which to characterise this. We define the RoI at a given time in the future, $R(T)$, as the ratio between its profits up until that point and its initial cost,
\begin{align}
R(T) = \frac{c_\text{profit}(T)}{c_\text{cost}(0)}.
\end{align}

Let the cost of the asset be the current spot price, as per the qubit asset pricing model (Def.~\ref{def:qubit_ass_pricing}). That is,
\begin{align}
c_\text{cost}(0) &= S_0 \nonumber \\
&= \sum_{t=0}^\infty D_t e^{-rt}.
\end{align}
Let the profit be the accumulated dividends, paid up until time $T$, using the same derivation technique that was applied to the qubit asset pricing model,
\begin{align}\index{Profit}
c_\text{profit}(T) &= \sum_{t=0}^T D_t e^{-rt}. \nonumber \\
\end{align}
Then the RoI is given by,
\begin{align}
	R(T) &= \frac{\sum_{t=0}^T D_t e^{-rt}}{\sum_{t=0}^\infty D_t e^{-rt}} \nonumber \\
	&= \frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}.
\end{align}
\comment{To do}

\begin{definition}[Return on investment]\index{Return on investment formula}
The net return on investment at time $T$, on the purchase of qubits, is given by,
\begin{align}
	R(T) = \frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}.
\end{align}
\end{definition}

\comment{Point at which it becomes negative!!}

\comment{Why is it independent of the scaling function? This is strictly less than unity. Is that reasonable? As T goes to infinity the ROI approaches unity. Or is this because efficient markets imply no profit?? In any case, this is a shit investment, no better than investment into classical technology.}

@@

\begin{table*}[!htb]
\caption{Summary of the dynamics of various economic models under several computational scaling functions of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network.} \label{tab:summary_ec_models}
\begin{tabular}{|p{0.255\linewidth}|p{0.22\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n^{}\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	Network price scaling factor (Sec.~\ref{sec:NPSF}) & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	Spot price of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_0=\frac{C_0}{f_\text{sc}(N_0)}\] & \[\frac{C_0}{N_0}\] & \[\frac{C_0}{{N_0}^p}\] & \[\frac{C_0}{e^{N_0}}\]\\
	\hline
	Future cost of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_t=\frac{C_0 {\gamma_C}^{-t}}{f_\text{sc}(N_0 {\gamma_N}^t)}
\] & \[\frac{C_0}{N_0{\gamma_N}^{t}{\gamma_C}^{t}}\] & \[\frac{C_0}{{N_0}^p{\gamma_N}^{pt}{\gamma_C}^t}\] & \[\frac{C_0}{\text{exp}(N_0{\gamma_N}^t){\gamma_C}^t}\]\\
	\hline
	Time-share computational power (Sec.~\ref{sec:arb_free_time_share}) & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	Single qubit leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n \cdot \text{exp}(N_0{\gamma_N}^t)}{N_0{\gamma_N}^t e^n}\]\\
	\hline
	Time-share spot price (Sec.~\ref{sec:time_share_spot}) & \[D_0=n C_0\] & \[nC_0\] & \[nC_0\] & \[nC_0\]\\
	\hline
	Computational dividend (Sec.~\ref{sec:comp_div}) & \[D_t=n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\]\\
	\hline
	Qubit asset price (Sec.~\ref{sec:qubit_pricing_model}) & \[S_0=n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\]\\
	\hline
	Forward contract price (Sec.~\ref{sec:for_contr}) & \[F(T)=n C_0 \frac{e^{-rT}{\gamma_C}^{-T}}{e^{r}\gamma_C-1}\] & \[n C_0 \frac{e^{-rT}{\gamma_C}^{-T}}{e^{r}\gamma_C-1}\] & \[n C_0 \frac{e^{-rT}{\gamma_C}^{-T}}{e^{r}\gamma_C-1}\] & \[n C_0 \frac{e^{-rT}{\gamma_C}^{-T}}{e^{r}\gamma_C-1}\]\\
	\hline
	Return on investment (Sec.~\ref{sec:ROI}) & \[R(T)=\frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}\] & \[\frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}\] & \[\frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}\] & \[\frac{e^{-r(T+1)}}{e^{r(T+1)}-{\gamma_C}^{T+1}}\]\\
	\hline
	Tax performance multiplier (Sec.~\ref{sec:taxation}) & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[{\gamma_T}^{-1}\] & \[{\gamma_T}^{-p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\end{table*}

>>>>

%
% Network Value
%

\subsection{Network value}\index{Network value}\label{sec:network_value}

The simplest economic metric one might define is the collective dollar value of the entire network. That is, the product of the number of qubits on the network and the dollar cost per physical qubit.

\begin{postulate}[Network value]\label{post:network_value}\index{Network value}
The dollar-value of the entire network is given by,
\begin{align}
	P_t &= C_t N_t \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

Note that the collective value of the network appreciates exponentially if the rate of network growth is greater than the rate of decay in the value of physical qubits, otherwise it depreciates. At \mbox{$\gamma_C=\gamma_N$} the network's value remains constant over time. This is shown in Fig.~\ref{fig:network_value}.

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{network_value}
	\caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below this it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}

@@

We begin by defining the ratio $Q_t$ between the economic return from executing computations, and the cost of the investment into physical hardware performing them,
\begin{align}
Q_t=\frac{n_\text{return}(t)}{n_\text{invest}(t)}.
\end{align}

Now, if \mbox{$Q=1$} we have the breakeven point, whereby investment into physical hardware is profit-neutral in payback. If \mbox{$Q<1$} we spend more on hardware than we gain from its use and run at a loss. But if \mbox{$Q>1$} we can make guaranteed profit by investing in new hardware. The perfect price competition assumption (Pos.~\ref{post:market_eff}) will drive the market price towards the zero-profit breakeven point (but not quite -- someone has to make money!), such that \mbox{$Q\gtrapprox 1$}. That is, the economic gain approximates the hardware investment, with \mbox{$Q\to 1$} driven ever closer to unity as market competition increases, thereby closing the gap between investment and reward,
\begin{align} \label{sec:gain_eq_invest}
	n_\text{return}(t) \gtrapprox n_\text{invest}(t).
\end{align}

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth})\index{Network growth postulate} and employing a combined computational scaling function\index{Combined computational scaling functions} (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is given by the network value (Pos.~\ref{post:network_value}),
\begin{align}
	n_\text{cost}(t) &= P_t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the time-dependent cost of computation postulate,

@@

This implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation is, measured in FLOPS per qubit,
\begin{align}
L_0 \gtrapprox \frac{C_0}{f_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the initial value of computations simply approximates the initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{cost_of_comp_n} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_n2} \\
\includegraphics[width=0.4\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}.}\label{fig:econ_cost_of_comp}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.42\textwidth]{single_qubit_QCL}
\caption{Time-dependent quantum computational leverage for a single qubit with different computational scaling functions, under the assumption of exponential network growth with \mbox{$N_0=1$}.}\label{fig:time_dep_QCL}
\end{figure}

@@

The computational dividend at future time $t$, $D_t$, is masterfully baked using the same recipe as the spot price\index{Jamie Oliver}, adjusted for extrapolated qubit growth and decay in the cost of computation,
\begin{definition}[Computational dividend]\label{def:dividend_formula}
The dollar-equivalent dividend paid by a time-share in the quantum network at future time $t$, for the duration of a single unit of time, is,
\begin{align} \label{eq:dividend}\index{Dividend}
D_t &= L_t c_n(t) \nonumber \\
&= n \frac{C_0{\gamma_C}^t}{N_0{\gamma_N}^t}.
\end{align}
\end{definition}
Up to normalisation this is equivalent to the network value (Pos.~\ref{post:network_value}). Note that the spot price, $D_0$, is the dividend at time \mbox{$t=0$}.

@@

The standard forward pricing model is \cite{???},
\begin{align} \label{eq:orig_for_contr} \index{Forward contract pricing model} 
F_T = D_0 e^{rT} - \sum_{t=1}^T D_t e^{r(T-t)},
\end{align}
where,
\begin{itemize}
	\item $F_T$ is the forward price at time $T$.\index{Forward price}
	\item $D_0$ is the spot price at time \mbox{$t=0$} (i.e present-day value).
	\item $T$ is the time of maturity, at which time the contract is executed and the transaction is made.\index{Maturity}
	\item $r$ is the risk-free rate of return. \index{Risk-free rate of return}
	\item The usual cost of carry, $q$, is neglected. We assume this is zero since maintenance of physical computer assets is somewhat negligible and the goods are effectively non-perishable. Furthermore, in the context of a global network, transactions may be executed entirely over the network, with no direct exchange in physical assets, making transactions very transparent and liquid, with little transaction overhead.\index{Cost of carry}
	\item $D_t$ is the expected dividend at time $t$. In our case this will be the dollar-equivalent value of units of computation.\index{Dividend}
\end{itemize}

@@

In our case, the spot price is that given by the qubit asset pricing model, and the dividends are the computational dividends in dollars. Then, from Eq.~(\ref{eq:orig_for_contr}), the forward price for qubits is,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in qubits is,
\begin{align}
F_T &= D_0 e^{rT} - \sum_{t=1}^T D_t e^{r(T-t)} \nonumber \\
&= n C_0 \left[e^{rT} + \frac{\gamma_C(e^{rT}-{\gamma_C}^T{\gamma_N}^{-T})}{N_0(\gamma_C - e^r\gamma_N)}\right].
\end{align}
\end{definition}

Note that in the limit of \mbox{$T\to 0$} this reduces to \mbox{$F_0 = D_0 = nC_0$}, which is simply the spot price of the asset.

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{forward_cont_pricing_mod}
\caption{Forward contract price on a single physical qubit to be delivered at time $T$ in the future. Units are \mbox{$C_0=1$}.\comment{Redo fig, outdated}}\label{fig:forward_cont_pricing_mod}
\end{figure}

@@

The return on investment (RoI) is a means by which to characterise this. We define the RoI at a given time in the future, $R(T)$, as the ratio between its profits up until that point and its initial cost,
\begin{align}
R_T = \frac{c_\text{profit}(T)}{c_\text{cost}(0)}.
\end{align}

Let the cost of the asset be the current spot price,
\begin{align}
c_\text{cost}(0) &= C_0.
\end{align}
Let the profit be the accumulated dividends, paid up until time $T$,
\begin{align}\index{Profit}
c_\text{profit}(T) &= \sum_{t=0}^T D_t e^{-rt}. \nonumber \\
\end{align}
Then the RoI is given by,
\begin{align}
	R_T = \frac{\sum_{t=0}^T D_t e^{-rt}}{C_0}.
\end{align}

\begin{definition}[Return on investment]\index{Return on investment formula}
The net return on investment at time $T$, on the purchase of qubits, is given by,
\begin{align}
	R_T &= \frac{\sum_{t=0}^T D_t e^{-rt}}{C_0}\nonumber \\
	&=\frac{e^{-rT}\gamma_C\left(\frac{\gamma_C}{\gamma_N}
	\right)^T - e^r\gamma_N}{N_0(\gamma_C-\gamma_N)}.
\end{align}
\end{definition}

@@

\begin{table*}[!htb]
\caption{Summary of the dynamics of various economic models under several computational scaling functions of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network.} \label{tab:summary_ec_models}
\begin{tabular}{|p{0.255\linewidth}|p{0.22\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n^{}\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	Network price scaling factor (Sec.~\ref{sec:NPSF}) & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	Spot price of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_0=\frac{C_0}{f_\text{sc}(N_0)}\] & \[\frac{C_0}{N_0}\] & \[\frac{C_0}{{N_0}^p}\] & \[\frac{C_0}{e^{N_0}}\]\\
	\hline
	Future cost of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_t=\frac{C_0 {\gamma_C}^{-t}}{f_\text{sc}(N_0 {\gamma_N}^t)}
\] & \[\frac{C_0}{N_0{\gamma_N}^{t}{\gamma_C}^{t}}\] & \[\frac{C_0}{{N_0}^p{\gamma_N}^{pt}{\gamma_C}^t}\] & \[\frac{C_0}{\text{exp}(N_0{\gamma_N}^t){\gamma_C}^t}\]\\
	\hline
	Time-share computational power (Sec.~\ref{sec:arb_free_time_share}) & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	Single qubit leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n \cdot \text{exp}(N_0{\gamma_N}^t)}{N_0{\gamma_N}^t e^n}\]\\
	\hline
	Time-share spot price (Sec.~\ref{sec:time_share_spot}) & \[D_0=n C_0\] & \[nC_0\] & \[nC_0\] & \[nC_0\]\\
	\hline
	Computational dividend (Sec.~\ref{sec:comp_div}) & \[D_t=n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\] & \[n C_0 {\gamma_C}^{-t}\]\\
	%\hline
	%Qubit asset price (Sec.~\ref{sec:qubit_pricing_model}) & \[S_0=n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\] & \[n C_0 \frac{e^r \gamma_C}{e^r \gamma_C - 1}\]\\
	\hline
	Forward contract price (Sec.~\ref{sec:for_contr}) & \[F_T\]=??? & ??? & ??? & ??? \\
	\hline
	Return on investment (Sec.~\ref{sec:ROI}) & \[R_T\]=??? & ??? & ??? & ???\\
	\hline
	Tax performance multiplier (Sec.~\ref{sec:taxation}) & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[{\gamma_T}^{-1}\] & \[{\gamma_T}^{-p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\end{table*}
